\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-19 NAR_DRAFT.tex
better

Figure \ref{NAR-ppv_fig} takes a consolidated view of classification accuracy and calibration in the portion of the posterior probability distribution relevant to clinicians and researchers.
For any probability between .6 and .95 \batcave is better calibrated than Mutect.
Essentially, for any posterior probability above .7 MuTect has a false positive rate around 8\%, which \batcave has a false positive rate that increases as posterior probability decreases.
The cost of this compression is recall, which is 3-5\% better than MuTect at 95\% posterior probability, and 3-7\% better at 90\%
At any posterior probability \batcave returns a larger fraction of all positive calls than MuTect.

>>>>

Figure \ref{NAR-ppv_fig} takes a consolidated view of classification accuracy and calibration in the portion of the posterior probability distribution relevant to clinicians and researchers.
For any probability between 60 and 95\% \batcave is better calibrated than Mutect.
Essentially, for any posterior probability above 70\% MuTect has a false positive rate around 8\%, while \batcave has a false positive rate that increases as posterior probability decreases.
The cost of this compression is recall, which is 3-5\% better than MuTect at 95\% posterior probability, and 3-7\% better at 90\%, depending on muation profile concentration.
At any posterior probability \batcave returns a larger fraction of all positive calls than MuTect.
